Final paper detail checks and analyses

### 2021-04-12 Final_analyses_checks_notebook.Rmd
checked proportion of people crossing diagnostic thresholds

alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))

@@

>>>>

alldat <-  readRDS(file = paste0(data_path, "four_cohorts_variables_exclusion.rds"))

@@

# change in thresholds in GLAD only

##1. Proportion scoring ≥10 on GAD-7 prepandemic

```{r GLAD prop GAD >10 prepandemic}

GLAD.prepan.GAD10 <-  GLAD.prepan %>%
  filter(gad.sum_score_prepan >=10) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(gad.sum_score_prepan)) %>%
  count()

print("proportion of GLAD sample with a GAD 7 score >= 10 prepandemic (i.e. and GLAD baseline)")
GLAD.prepan.GAD10 / GLAD.base

## 2. Proportion scoring ≥10 on GAD-7 current/baseline

```{r GLAD prop GAD >10 pandemic baseline}

GLAD.base.GAD10 <-  GLAD.prepan %>%
  filter(gad.sum_score_base >=10) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(gad.sum_score_base)) %>%
  count()

print("proportion of GLAD sample with a GAD 7 score >= 10 at the pandemic baseline")
GLAD.base.GAD10 / GLAD.base

```
## 3. Proportion scoring ≥ 10 on PHQ-9 prepandemic

```{r GLAD prop PHQ >10 prepandemic}

GLAD.prepan.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_prepan >=9) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(phq.sum_score_prepan)) %>%
  count()

print("proportion of GLAD sample with a PHQ 9 score >= 10 at the pandemic baseline")
GLAD.prepan.PHQ9 / GLAD.base

## 4. Proportion scoring ≥ 10 on PHQ-9 current/baseline

```{r GLAD prop PHQ >10 pandemic baseline}

GLAD.base.PHQ9 <-  GLAD.prepan %>%
  filter(phq.sum_score_base >=9) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(phq.sum_score_base)) %>%
  count()

print("proportion of GLAD sample with a PHQ 9 score >= 10 at the pandemic baseline")
GLAD.base.PHQ9 / GLAD.base

```
## 5. Proportion scoring ≥ 14 on PCL-6 prepandemic

```{r GLAD prop PCL >14 pre pandemic}

GLAD.prepan.PCL <-  GLAD.prepan %>%
  filter(pcl.sum_score_prepan >=14) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(pcl.sum_score_prepan)) %>%
  count()

print("proportion of GLAD sample with a PCL score >= 14 at the pandemic baseline")
GLAD.prepan.PCL / GLAD.base

## 6. Proportion scoring ≥ 14 on PCL-6 current/baseline

```{r GLAD prop PCL >14 pandemic baseline}

GLAD.base.PCL <-  GLAD.prepan %>%
  filter(pcl.sum_score_base >=14) %>%
  count()

GLAD.base <-  GLAD.prepan %>%
  filter(!is.na(pcl.sum_score_base)) %>%
  count()

print("proportion of GLAD sample with a PCL score >= 14 at the pandemic baseline")
GLAD.base.PCL / GLAD.base

## RAMP PCL endorsement rate at pandemic baseline

```{r}

RAMP.retro.PCL <-  RAMP.retro %>%
  filter(pcl.sum_score_base >=14) %>%
  count()

RAMP.base <-  RAMP.retro %>%
  filter(!is.na(pcl.sum_score_base)) %>%
  count()

print("proportion of RAMP sample with a PCL score >= 14 at the pandemic baseline")
RAMP.retro.PCL / RAMP.base

## NBR PCL endorsement rate at pandemic baseline

```{r}

NBR.retro.PCL <-  NBR.retro %>%
  filter(pcl.sum_score_base >=14) %>%
  count()

NBR.base <-  NBR.retro %>%
  filter(!is.na(pcl.sum_score_base)) %>%
  count()

print("proportion of NBR sample with a PCL score >= 14 at the pandemic baseline")
NBR.retro.PCL / NBR.base
